---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![R build status](https://github.com/MarselScheer/Rpkgtemplate/workflows/R-CMD-check/badge.svg)](https://github.com/MarselScheer/Rpkgtemplate/actions)
[![Coverage Status](https://img.shields.io/codecov/c/github/MarselScheer/Rpkgtemplate/develop.svg)](https://codecov.io/github/MarselScheer/Rpkgtemplate?branch=develop)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/Rpkgtemplate)](https://cran.r-project.org/package=Rpkgtemplate)
[![metacran downloads](https://cranlogs.r-pkg.org/badges/Rpkgtemplate)](https://cran.r-project.org/package=Rpkgtemplate)


# TODOs for using the Rpkgtemplate

After copying the files from this template the
package names has to be updated in 

- README.Rmd (also the badges)
- Makefile

The CI-pipeline will create a pkgdown site that is deployed
to the branch 'gh-pages'. Just go to the settings and specify
that branch on the 'pages'-entry to make the pkgdown-site
accessible. In order to avoid to fetch the origin/gh-pages
one can modify the git-config:

	git config -e

and then add

```
[remote "origin"]
	...
    fetch = +refs/heads/main:refs/remotes/origin/main
    fetch = +refs/heads/develop:refs/remotes/origin/develop
    fetch = +refs/heads/feature/*:refs/remotes/origin/feature/*
```

In newer versions of git (probably >= 2.29) it should be also 
possible to exclude certain branches from fetch, like:

```
[remote "origin"]
	...
    fetch = ^refs/heads/gh-pages
```


# $Rpkgtemplate

Standardizes the my personal R-packages on github.

## Installation

You can install it from CRAN

```{r, eval = FALSE}
install.packages('$Rpkgtemplate')
```

or github

```{r gh-installation, eval = FALSE}
remotes::install_github('MarselScheer/$Rpkgtemplate')
```

# Package development
## docker-folder

The dockerfile defines an image that provides an RStudio
server and an emacs installation. The script start.sh
starts the container in a way that allows run the emacs
on the X11-system of the host system. By default the folder
'~/docker_fs' from the host system is mounted into the 
docker container and links '.emacs.d, .ssh, .gitconfig'
from the 'docker_fs'-folder into the home folder of the 
user 'rstudio' of the docker container.

## renv

The package renv is used to easily install all packages
that are necessary for package development. It is not
used in the CI-pipeline.

# sessionInfo

```{r}
sessionInfo()
```
