---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![R build status](https://github.com/MarselScheer/Rpkgtemplate/workflows/R-CMD-check/badge.svg)](https://github.com/MarselScheer/Rpkgtemplate/actions)
[![Coverage Status](https://img.shields.io/codecov/c/github/MarselScheer/Rpkgtemplate/develop.svg)](https://codecov.io/github/MarselScheer/Rpkgtemplate?branch=develop)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/Rpkgtemplate)](https://cran.r-project.org/package=Rpkgtemplate)
[![metacran downloads](https://cranlogs.r-pkg.org/badges/Rpkgtemplate)](https://cran.r-project.org/package=Rpkgtemplate)


# TODOs for using the Rpkgtemplate

After copying the files from this template the
package names has to be updated in 

- README.Rmd (also the badges)
- Makefile

The CI-pipeline will create a pkgdown site that is deployed
to the branch 'gh-pages'. Just go to the settings and specify
that branch on the 'pages'-entry to make the pkgdown-site
accessible.

# $Rpkgtemplate

Standardizes the my personal R-packages on github.

## Installation

You can install it from CRAN

```{r, eval = FALSE}
install.packages('$Rpkgtemplate')
```

or github

```{r gh-installation, eval = FALSE}
remotes::install_github('MarselScheer/$Rpkgtemplate')
```

# sessionInfo

```{r}
sessionInfo()
```
